---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# gatherer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/gatherer)](https://CRAN.R-project.org/package=gatherer)
<!-- badges: end -->

The goal of gatherer is to programmatically create and edit maps on gather.town. This package is in pre-alpha and is probably non-functional.

## Installation

The development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("remotes")
remotes::install_github("andrewpbray/gatherer")
```

## Creating a map

A good starting point for your map is one of the built-in templates. To load the basic lab classroom template, first attach the package, then run `create_from_template()`.

```{r}
library(gatherer)
my_lab <- create_from_template(template = "lab")
```

Which creates a new map object that you can inspect, edit, and eventually push to gather.town. You can plot the background image of the map

```{r}
plot(my_lab)
```

as well as query a summary of its properties:

```{r}
summary(my_lab)
```


## Host your map on gather.town

### Step one: configure your map

The minimal information that gather.town needs to know includes the name of the map (`map_id` and the name of the space that it belongs to. You'll also need to pass it your API key, which you can request when you set up an account on [gather.town](gather.town) (this functionality is pending).
.

1. `map_id` is 
2. `space_id` 

```{r}
gather_config(map = my_lab, 
              map_id = map_id, 
              space_id = space_id, 
              api_key = api_key)
```

### Step two: push your map to gather.town


```{r}
push_map(my_lab)
```


## Customize your map






